A mechanization of semi-simplicial and semi-cubical sets in the calculus of inductive constructions

### 2022-09-09 paper/paper.tex
paper: typeset definition of coh2

\subsection{Semi-cubical sets}
We might naively attempt to define $\Cube{}$ identically to \DeltaHat, but let us briefly explain why this wouldn't work, motivating the definition of semi-cubical sets as in \cite{Antolini00}. If there were morphisms from every $\sq{m}$ to \sq{n}, we would end up with:

$$
  \begin{tikzcd}
    \bullet \arrow[r] \arrow[dr] \arrow[d] & \bullet \arrow[d] \\
    \bullet \arrow[r] \arrow[ur] & \bullet
  \end{tikzcd}
$$

where the filling conditions are conflated with the cube itself. $\Simplex{n}$ can be defined quite simply as the convex hull of $n$ points, but even defining the standard $n$-cube becomes a problem if we unittypet with $\sq{n}$, but the situation becomes much more amenable if we define:

\begin{definition}[\Cube{n}]
  \begin{equation*}
    \Cube{n} := \I{n} = \sq{0, 1}^n
  \end{equation*}
\end{definition}

@@

>>>>

\subsection{Semi-cubical sets}
\begin{definition}[\Cube{n}]
  \begin{equation*}
    \Cube{n} := \I{n} = \sq{0, 1}^n
  \end{equation*}
\end{definition}

@@

where $\cohtwo{frame}$ is:

\begin{align*}
  \cohf[m][\omega][\theta][r][p][n][p][][d = {\restrf[m][\epsilon][q+2][n][p][][d = \d, D = \D]}, D = \D]\;\bullet         \\
  \ap (\restrf[m][\omega][r][n][p][][d = {\cohf[m][\epsilon][\theta][q+1][p][n][p][][d = \d, D = \D]}, D = \D]\;\bullet    \\
  \cohf[m][\epsilon][\omega][q][r][n][p][][d = {\restrf[m][\theta][p][n][p][][d = \d, D = \D]}, D = \D] =                  \\
  \ap (\restrf[m][\theta][p][n][p][][d = {\cohf[m][\epsilon][\omega][q+1][r+1][n][p][][d = \d, D = \D]}, D = \D])\;\bullet \\
  \cohf[m][\epsilon][\theta][q][p][n][p][][d = {\restrf[m][\omega][r+1][n][p][][d = \d, D = \D]}, D = \D]\;\bullet         \\
  \ap (\restrf[m][\epsilon][q][n][p][][d = {\cohf[m][\omega][\theta][r][p][n][p][][d = \d, D = \D]}, D = \D])
\end{align*}
